Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-08 referee.tex
Referee response: Formatting changes. Adding intro sentences.

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}

@@

\definecolor{verbgray}{gray}{0.9}
\lstnewenvironment{referee}{%
  \lstset{backgroundcolor=\color{verbgray},
  frame=single,
  framerule=0pt,
  basicstyle=\ttfamily,
  columns=fullflexible}}{}

@@

@@

\begin{referee}
Major comments:
1) One of the main points of the paper is studying the multiplicity of Pop III 
stars in a halo. This multiplicity might be due to the fact that Pop III stars 
have collapsed to a BH after their lifetime and a second Pop III star could form
 in the same halo. This is very plausible. If several Pop III stars are found 
 forming in the same halo at the same time, however, the employed star particle 
 algorithm has a hard-coded length scale of 1pc in which only one star particle 
 can be formed. I am wondering if this is an effect that is resolution dependent 
 - do the same number of stars form if the resolution is increased and the 
 maximum distance is decreased? Which is the motivation for the length scale of 
 1pc?
\end{referee}

@@

\begin{referee}
Minor comments:
The authors should state at one point in the paper for which properties they use
 comoving or physical units.
\end{referee}
-Clarified this at the end of the second paragraph in the Simulation Setup section.

\begin{referee}
Introduction:
The authors write that Pop III star formation is generally more massive. While a
 fraction of the community agrees with that, there is manifoldly cited work that
  finds low-mass Pop III progenitors, and the authors should not let that 
  unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
\end{referee}
-I will look at and add these citations and detail to the introduction.

@@

\begin{referee}
Methods:
In Wise+12, three different environment regions are picked. Please provide more 
description on the rare peak simulation here and discuss why this one is 
appropriate in this context.
\end{referee}
-RP stands for radiation pressure in Wise+12 (correct?), not rare peak. The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmo parameters.

@@

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star 
formation? How many Pop III stars form between Z=0 and Z=5e-6 Z_sol?
\end{referee}
-Simulation question

@@

\begin{referee}
Results:
Figure 2 is quite empty, it would be useful to include the halo mass function of
 the earliest Pop III formation redshift with its analytic prediction. In 
 addition, the authors could provide a line or an arrow to show their halo mass 
 resolution limit.
\end{referee}
-As far as the HMF of the earliest Pop III formation redshift, is this referring to the HMF at the time when Pop III stars first begin to form, so at about z=27, what is the HMF at that time and how does it compare with Sheth-Tormen? I will plot this up.

@@

\begin{referee}
Discussion:
The authors give three reasons for the halo mass spread. Can they estimate which
 of the three processes (BH formation, dynamical heating and temporal LWBG 
 fluctuations) is responsible for the spread by which fraction?
\end{referee}
-It's not immediately obvious to me how we would be able to estimate this. I would have to look at these processes in more detail to see if there are some mass ranges correlated with them. Any insight from John?

>>>>

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage{mdframed}

@@

\definecolor{quotegray}{gray}{0.9}
% \lstnewenvironment{referee}{%
%   \lstset{backgroundcolor=\color{quotegray},
%   frame=single,
%   framerule=0pt,
%   basicstyle=\ttfamily,
%   columns=fullflexible}}{}

% https://tex.stackexchange.com/questions/111065/quoting-styles-technical-an-appreciation-questions
\mdfdefinestyle{myquotestyle}{
  leftmargin=15pt,
  rightmargin=15pt,
  backgroundcolor=quotegray,
  linewidth=0pt,
  skipbelow=\topskip,
  skipabove=\topskip
}
\newenvironment{referee}[1][]{%
    \ignorespaces%
    \begin{mdframed}[style=myquotestyle,#1]%
}{%
    \end{mdframed}%
    \ignorespacesafterend%
}%

% \newenvironment{referee}[1][]{
%   \ignorespaces%
%   \begin{mdframed}[style=myquotestyle,#1]%
% }{%
%   \end{mdframed}%
%   \ignorespaceafterend%
% }%

@@

We thank the referee for their insightful review.  Their review is directly quoted below in the gray boxes with our responses below.  Any changes to the manuscript has been \textbf{bold-faced}.

@@

\begin{referee}
Major comments:

1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo. This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo. This is very plausible. If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed. I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased? Which is the motivation for the length scale of 1pc?
\end{referee}

@@

\begin{referee}
Minor comments:

The authors should state at one point in the paper for which properties they use comoving or physical units.
\end{referee}
-Clarified this at the end of the second paragraph in the Simulation Setup section.

\begin{referee}
Introduction:

The authors write that Pop III star formation is generally more massive. While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
\end{referee}
-I will look at and add these citations and detail to the introduction.

@@

\begin{referee}
Methods:

In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}
-RP stands for radiation pressure in Wise+12 (correct?), not rare peak. The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmo parameters.

@@

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}
-Simulation question

@@

\begin{referee}
Results:

Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction. In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
\end{referee}
-As far as the HMF of the earliest Pop III formation redshift, is this referring to the HMF at the time when Pop III stars first begin to form, so at about z=27, what is the HMF at that time and how does it compare with Sheth-Tormen? I will plot this up.

@@

\begin{referee}
Discussion:

The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}
-It's not immediately obvious to me how we would be able to estimate this. I would have to look at these processes in more detail to see if there are some mass ranges correlated with them. Any insight from John?
